Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-10-07 paper/virtual_cytoplasm_v2.tex
answered some of the comments

In this work, we report an all-atom model of part of the cytoplasm of
\textit{Escherichia coli} was built to reflect the real biological
system, in particular as regards a realistic composition of this
``soup''. We discuss the difficulties that arise when building such a
system and provide a set of Python scripts and files that anyone can
use to build its own crowded systems with custom parameters and
compounds. Additionally, we performed long molecular dynamics
simulations of our cytoplasm model, reaching \SI{3}{\micro\second} of
total simulation time. This work is the first to explore the
structural dynamics of an all-atom explicit solvent cytoplasm model
with microsecond scale molecular dynamics simulations. {\bf IS THAT
  REALLY TRUE? A REFEREE MAY GET ANGRY WHEN READING THIS.}

@@

\subsection{Analyses}
For statistics, the average and standard error {\bf standard error or
  deviation?} of the three trajectories are reported. For values that
are specific to each chain, we used the average over the individual
chains in each trajectory of the replicas. Additionally, since there
is more than one copy of some crowders in the cytoplasm models,
average values and standard errors are calculated {\bf DO YOU MEAN THE
  AVERAGE OVER ALL COPIES? considering each copy and each replica}
independently. As in the dilute system, separate chains of each copy
of the crowders were considered as independent samples when running
analyses that focus on one single chain. The first half of all
simulations was discarded as equilibration time and analyses used only
the second half.

Analyses were done using GROMACS tools after removing artifacts
generated by periodic boundary conditions from the trajectories. A
Mean Square Displacement (MSD) analysis was performed to calculate the
translational diffusion coefficient, which were extracted by a linear
fit to MSD by averaging blocks with a length of {\bf 10 ns even for
  proteins?}  $10\,ns$~\cite{Allen1987a}. In principle, diffusion
coefficient needs to be corrected for finite size
effects~\cite{Yeh2004} but due to relatively large simulation boxes
this correction is negligible {\bf NOT FOR PROTEINS THAT DIFFUSE
  SLOWLY!}. Root Mean Square Deviation (RMSD) and Root Mean Square
Fluctuation (RMSF) calculations considered the C$\upalpha$ atoms only
and the reference frame for RMSF was the midpoint of the time interval
{\bf ARE YOU SURE? THE DEFAULT IS TO TAKE THE AVERAGE STRUCTURE. OR DO
  YOU MEAN THE STRUCTURE FOR FITTING?} used for analysis in each
trajectory. The chain interface area of a given oligomer in a given
frame was calculated as the difference between the solvent exposed
surface area (SASA) of the oligomer in that frame and the sum of the
SASAs of each of its chains independently in that same frame. Other
analyses, such as box volume and Radial Distribution Function (RDF),
followed standard procedures.

@@

\begin{table}[H]
\centering
\caption{Protein, PDB ID, number N of proteins in the simulation. 
Fraction of the total abundance of non-ribosomal proteins in the cytosol of {\em
    E. coli} K12 and oligomeric state of each protein that was
  selected to compose our cytoplasm model. {\bf WRITE OUT WHOLE
    PROTEIN NAMES}}
\label{tbl:protein_fraction}
\begin{tabular}{lcccc}
\hline
Protein & PDB & N & Fraction [\%] & State\\
\hline
TufA & 1DG1~\cite{Abel1996}       & 6 & 19.7 &  dimer \\
MetE & 1U22~\cite{Ferrer2004}     & 7 & 11.6 &  monomer \\
IcdA & 1P8F~\cite{Mesecar2000}    & 2 & 4.7  &  dimer \\
AhpC & 1YEP~\cite{Parsonage2005}  & 1 & 4.1  &  decamer \\
CspC & 1MJC~\cite{Schindelin1994} & 3 & 4.0  &  monomer \\
Ppa  & 2EIP~\cite{Kankare1996}    & 1 & 2.9  &  hexamer \\
GapA & 1S7C~\cite{ShinXXX}        & 1 & 2.1  &  tetramer \\
Eno  & 1E9I~\cite{Kuhnel2001}     & 1 & 1.9  &  dimer \\
\hline
Total &                           & 48& 51.1 & \\
\hline
\end{tabular}
\end{table}

@@

\subsubsection{Structural integrity}
The structure of the individual chains of the crowders that were used
in our cytoplasm model were not affected to a great extent by the
crowded environment. The value of the root mean square deviation
(RMSD, Fig.~\ref{fig:structural_integrity_chain}A) considering only
their C$\upalpha$ in the cytoplasm model is within 11\% of its value
under dilute conditions {\bf WHAT DOES WITHIN 11\% MEAN?}, except for
TufA, MetE and IcdA, which have RMSD values 105, 25 and 33\% higher in
the crowded environment than in the dilute condition. {\bf ARE THERE
  RMSD PLOTS? REFER TO THEM.} Visual inspection of their trajectories
showed that there is partial unfolding of their N- or C-terminal
residues. {\bf IS THERE A KNOWN PHYSIOLOGICAL REASON FOR THAT?. IS
  MetE A MULTIDOMAIN PROTEIN WHERE DOMAINS MOVE WITH RESPECT TO EACH
  OTHER?}

@@

To the best of our knowledge, {\bf AGAIN CHECK LATEST FEIG PAPERS}
there is only published study on large scale cytoplasm models that
included metabolites with all-atom explicit solvent molecular
dynamics~\cite{Yu2016a}. Although these authors did not report
aggregation, they mention that the translational diffusion of highly
charged phosphate-containing metabolites is ``much slower'' than
expected in their system. They attributed this observation to
non-specific interactions between such metabolites and proteins. Maybe
aggregation also contributed to their slower diffusion but it was not
evident during their \SI{140}{\nano\second} simulation.

>>>>

In this work, we report an all-atom model of part of the cytoplasm of
\textit{Escherichia coli} was built to reflect the real biological
system, in particular as regards a realistic composition of this
``soup''. We discuss the difficulties that arise when building such a
system and provide a set of Python scripts and files that anyone can
use to build its own crowded systems with custom parameters and
compounds. Additionally, we performed long molecular dynamics
simulations of our cytoplasm model, reaching \SI{3}{\micro\second} of
total simulation time. This work is the first to explore the
structural dynamics of an all-atom explicit solvent cytoplasm model {\color{blue} of {\em E. coli}}
with microsecond scale molecular dynamics simulations. {\bf IS THAT
  REALLY TRUE? A REFEREE MAY GET ANGRY WHEN READING THIS.}

@@

\subsection{Analyses}
For statistics, the average and standard error {\bf standard error or
  deviation? \color{blue} standard error} of the three trajectories are reported. For values that
are specific to each chain, we used the average over the individual
chains in each trajectory of the replicas. Additionally, since there
is more than one copy of some crowders in the cytoplasm models,
average values and standard errors are calculated {\bf DO YOU MEAN THE
  AVERAGE OVER ALL COPIES? considering each copy and each replica}
independently. As in the dilute system, separate chains of each copy
of the crowders were considered as independent samples when running
analyses that focus on one single chain. The first half of all
simulations was discarded as equilibration time and analyses used only
the second half.

Analyses were done using GROMACS tools after removing artifacts
generated by periodic boundary conditions from the trajectories. A
Mean Square Displacement (MSD) analysis was performed to calculate the
translational diffusion coefficient, which were extracted by a linear
fit to MSD by averaging blocks with a length of $10\, ns$ for dilute systems and $100\, ns$ 
for cytoplasm system~\cite{Allen1987a}. In principle, diffusion
coefficient needs to be corrected for finite size
effects~\cite{Yeh2004} but due to relatively large simulation boxes
this correction is negligible {\bf NOT FOR PROTEINS THAT DIFFUSE
  SLOWLY!}. Root Mean Square Deviation (RMSD) and Root Mean Square
Fluctuation (RMSF) calculations considered the C$\upalpha$ atoms only
and the reference frame for RMSF was the midpoint of the time interval
{\bf ARE YOU SURE? THE DEFAULT IS TO TAKE THE AVERAGE STRUCTURE. OR DO
  YOU MEAN THE STRUCTURE FOR FITTING?} used for analysis in each
trajectory. The chain interface area of a given oligomer in a given
frame was calculated as the difference between the solvent exposed
surface area (SASA) of the oligomer in that frame and the sum of the
SASAs of each of its chains independently in that same frame. Other
analyses, such as box volume and Radial Distribution Function (RDF),
followed standard procedures.

@@

\begin{table}[H]
\centering
\caption{Protein, PDB ID, number N of proteins in the simulation. 
Fraction of the total abundance of non-ribosomal proteins in the cytosol of {\em
    E. coli} K12 and oligomeric state of each protein that was
  selected to compose our cytoplasm model. {\bf WRITE OUT WHOLE
    PROTEIN NAMES}}
\label{tbl:protein_fraction}
\begin{tabular}{ccccc}
\hline
Protein & PDB & N & Fraction [\%] & State\\
\hline
{\color{blue}Elongation factor TU} (TufA) & 1DG1~\cite{Abel1996}       & 6 & 19.7 &  dimer \\
{\color{blue}Cobalamin-independent methionine synthase} (MetE) & 1U22~\cite{Ferrer2004}     & 7 & 11.6 &  monomer \\
{\color{blue}Isocitrate dehydrogenase} (IcdA) & 1P8F~\cite{Mesecar2000}    & 2 & 4.7  &  dimer \\
{\color{blue}Alkyl hydroperoxide reductase subunit C} (AhpC) & 1YEP~\cite{Parsonage2005}  & 1 & 4.1  &  decamer \\
{\color{blue}Cold-shock protein} (CspC) & 1MJC~\cite{Schindelin1994} & 3 & 4.0  &  monomer \\
{\color{blue}Pyrophosphatase} (Ppa)  & 2EIP~\cite{Kankare1996}    & 1 & 2.9  &  hexamer \\
{\color{blue}Glyceraldehyde 3-phosphate dehydrogenase A} (GapA) & 1S7C~\cite{ShinXXX}        & 1 & 2.1  &  tetramer \\
{\color{blue}Enolase} (Eno)  & 1E9I~\cite{Kuhnel2001}     & 1 & 1.9  &  dimer \\
\hline
Total &                           & 48& 51.1 & \\
\hline
\end{tabular}
\end{table}

@@

\subsubsection{Structural integrity}
The structure of the individual chains of the crowders that were used
in our cytoplasm model were not affected to a great extent by the
crowded environment. The value of the root mean square deviation considering only
their C$\upalpha$ in the cytoplasm model is within 11\% of its value
under dilute conditions {\bf WHAT DOES WITHIN 11\% MEAN?}, except for
TufA, MetE and IcdA, which have RMSD values 105, 25 and 33\% higher in
the crowded environment than in the dilute condition {\color{blue}(Fig.~\ref{fig:structural_integrity_chain}A)}. {\bf ARE THERE
  RMSD PLOTS? REFER TO THEM.} Visual inspection of their trajectories
showed that there is partial unfolding of their N- or C-terminal
residues. {\bf IS THERE A KNOWN PHYSIOLOGICAL REASON FOR THAT?. IS
  MetE A MULTIDOMAIN PROTEIN WHERE DOMAINS MOVE WITH RESPECT TO EACH
  OTHER?}

@@

To the best of our knowledge, {\bf AGAIN CHECK LATEST FEIG PAPERS} {\color{blue} Latest Feig paper is not a cytoplasm model~\cite{nawrocki2019}}
there is only published study on large scale cytoplasm models that
included metabolites with all-atom explicit solvent molecular
dynamics~\cite{Yu2016a}. Although these authors did not report
aggregation, they mention that the translational diffusion of highly
charged phosphate-containing metabolites is ``much slower'' than
expected in their system. They attributed this observation to
non-specific interactions between such metabolites and proteins. Maybe
aggregation also contributed to their slower diffusion but it was not
evident during their \SI{140}{\nano\second} simulation.
